% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Drew P. Short}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
 

\begin{letter}{
Mozilla Corporation \\
331 E. Evelyn Avenue \\
Mountain View, CA 94041}


\begin{flushleft}
{\large\bf Drew P. Short}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
\hfill 1430 Taylor Ave W, Saint Paul, MN 55104 \\
\hfill (651) 285-4565 
\end{flushright} 
\vfill % forces letterhead to top of page

 
\opening{Dear Hiring Manager for the Research Engineer Position:} 
 
\noindent I found your open Research Engineer position through the
Mozilla career site and am applying because this role aligns with my
future goals as a software engineer. As a loyal user of Mozilla
products I deeply resonate with Mozilla's goal of building a better
Internet and am excited about the possibility to work for a company
that has changed the Internet so profoundly.
 
\noindent For the past 3 years I have been expanding and maintaining
a large Java Spring web application for Cargill Inc. Risk Management.
This has made me sensitive to the difficulties in providing a unified
experience on the web. I would like to use my skills and ambitions
to make the web a better place for everyone; developers, designers and users
alike. I have hobbyist experience with Rust and love the work I
have done in the language so far, I think it has a very bright future
ahead of it.
 
\noindent I would love to have an opportunity to share my experience,
discuss the position, and explore the unique background I can bring
to the team.
 
\closing{Thanks for your time,} 
 

 
%\encl{}  				% Enclosures

\end{letter}
 

\end{document}






