% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font
\usepackage{fancyhdr}  % FancyHDR package for footers 
\usepackage{hyperref}  % HyperRef package to get fancy hyperlinks
\usepackage{ marvosym } % Symbol library

% Hyperref setup
\hypersetup{
	colorlinks=true,
	urlcolor=blue
}

\pagestyle{fancy}
\rfoot{Last Updated: \today}

\begin{document}

\name{Drew P. Short}
% \address used twice to have two lines of address
\address{1430 Taylor Ave W, St. Paul, MN 55104}
\address{
    \Mobilefone \hspace{1 pt} (651)-285-4565 | 
    \Letter \hspace{1 pt} \href{mailto:drew@sothr.com?subject=Concerning Your Resume}{drew@sothr.com} | 
    \Mundus \hspace{1 pt} \url{https://www.sothr.com}
}

\begin{resume}

\section{OBJECTIVE} A development position on a software engineering team, with special 
                interests in web development, middleware, and backend processing systems. 

\section{EDUCATION} {\sl Bachelor of Science,} Information Technology \\
                % \sl will be bold italic in New Century Schoolbook (or
	            % any postscript font) and just slanted in
		        % Computer Modern (default) font
                Minnesota State University Mankato, Mankato, MN 
                Graduated May 2013 \\
                Concentration: Software Engineering \\
                Minor: Ethics 

\section{COMPUTER \\ SKILLS} {\sl Languages \& Software:} Java, SQL, Scala, Javascript, 
         Ruby, Rust, Python, C\#, C, Spring Framework, JEE, 
                Hibernate, JUnit, Log4J, Logback, SLF4J, 
                Backbone.js, JQuery, Bootstrap, 
                Oracle, MySQL, MariaDB, MSSQL, SQLite. \\
                {\sl Operating Systems:} Windows, Linux (Arch, Ubuntu, RHEL, OpenSuse), OSX.

\section{EXPERIENCE} {\sl Java Developer} \hfill 2013 - Present (2 Years, 4 Months) \\
                Cargill Incorporated,
                Risk Management, Hopkins, MN 
                \begin{itemize}  \itemsep -2pt % reduce space between items
                \item Designed, implemented, and tested the most complex, 
                    Risk Product to date within the restrictions of the original 
                    system.
                \item Migrated a Spring web application to the latest version 
                    of JQuery, rewrote custom plugins, and re-organized the 
                    structure to comply with standards.
                \item Helped rewrite and upgrade a system designed to manage 
                    Risk Products and give the end user control over the
		    individual flow components.
                \item Maintained and improved upon a Spring web application 
                    that has been in use for 10+ years. Modernized components, 
                    improved the backend, and implemented modern front-end 
                    components for existing functionality. 
                \end{itemize}
 
                {\sl Software Engineer Intern} \hfill            2011 - 2013 (2 Years, 1 Month) \\
                Information Technology Department, Minnesota State University Mankato, \\
                Contracted to FPX LLC, Mankato, MN 
                \begin{itemize}  \itemsep -2pt %reduce space between items
                \item Developed software that permutates pre-selected data for 
                    automated testing. 
                \item Expanded a REST API and implemented continuous 
                    integration testing. 
                \item Developed a domain specific language for internal 
                     verification, testing and reporting tools. 
                \item Developed a 'playback' system that enabled 're-playing' 
                    data to allow for duplication and debugging of client bugs. 
                \item Quality assurance, code coverage and regression unit testing. 
                \end{itemize} 

                {\sl Geek Squad Agent} \hfill        2008 - 2011 (3 Years, 1 Month) \\
                Best Buy, Blaine, MN \\
                Best Buy, Mankato, MN 
                \begin{itemize}  \itemsep -2pt %reduce space between items
                \item Senior Technician. Responsible for overseeing, 
                    repairs in the precinct. 
                \item Provide technical support for Best Buy customers
		    and persue software and hardware sale opportunities.
                \end{itemize} 

\section{AWARDS, \\ MEMBERSHIPS, \\ AND TRAINING}
            	\begin{itemize}  \itemsep -2pt %reduce space between items
                \item Eagle Scout \hfill 2007
            	\item IEEE Member \hfill 2009-2011
            	\item BSA Leadership Instructor \hfill Summers 2004-2007
            	\item Attended NAYLE Leadership Course \hfill Summer 2006
                \end{itemize}


\end{resume}
\end{document}
